### 2024-06-04 thesis/input_files/literaturereview.tex
cleaned all problems and warnings

During the past 25 years a wide range of new ideas have been proposed for electricity point forecasting and for probabilistic forecasting. The field benefitted greatly from the increase of computing power, the greater availability of data and the interest in data science. As a consequence, the forecaster's toolbox has grown in size and complexity. Before delving into the literature review, we stress that at this point in time there is no superior method. Different solutions may outperform or underperform compared to other techniques depending on the problem settings. Thus, understanding the complexity, strengths and weaknesses of each method is crucial for fitting the right model to the right setting. Within this research community, the need for more homogeneity in the choice of the error valuation metrics emerged (Section \ref{metrics}), data quality and in the way of comparing model performances \cite{EPF_review}. As a solution, \cite{lago} proposes a checklist to aid evaluating the meaningfulness of new research. Throughout this thesis work, we will stick to the proposed principles and best practices peculiar of the EF field.
%literature review

>>>>

During the past 25 years a wide range of new ideas have been proposed for electricity point forecasting and for probabilistic forecasting. The field benefitted greatly from the increase of computing power, the greater availability of data and the interest in data science. As a consequence, the forecaster's toolbox has grown in size and complexity. Before delving into the literature review, we stress that at this point in time there is no superior method. Different solutions may outperform or underperform compared to other techniques depending on the problem settings. Thus, understanding the complexity, strengths and weaknesses of each method is crucial for fitting the right model to the right setting. Within this research community, the need for more homogeneity in the choice of the error valuation metrics emerged, see Section \ref{metrics}, along with the need of higher data quality and uniformity in the way of comparing model performances \cite{EPF_review}. As a solution, \cite{lago} proposes a checklist to aid evaluating the meaningfulness of new research. Throughout this thesis work, we will stick to the proposed principles and best practices peculiar of the EF field.
%literature review
